Model LF

### 2023-03-17 paper version Hamid new test.Rmd
commit

@@

COMMENT> 
IDENTITY> alpha
EQ> alpha = 1
IF> TSLAG(wage_gap1,4) >= wage_ben_gap_mean
IDENTITY> alpha
EQ> alpha = 0
IF> TSLAG(wage_gap1,4) < wage_ben_gap_mean

@@

  shock_wage_ds_model  = TIMESERIES(c(shock_wage_ds_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens_3 = TIMESERIES(c(sens_3),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4),
   alpha = TIMESERIES(c(alpha),   
                       START=c(2005,2),FREQ=4),
  wage_ben_gap_mean = TIMESERIES(c(wage_ben_gap_mean),   
                       START=c(2005,2),FREQ=4)
  )
```

@@

S_modelData$wage_ben_gap_mean = wage_ben_gap_mean

@@

pc_ds_bs1 = Shock_bs1$simulation$pc_ds

@@

inflation_01= Shock_1$simulation$inflation
pc_ds_01= Shock_1$simulation$pc_ds
alpha_01 = Shock_1$simulation$alpha
y_01= Shock_1$simulation$y
max_dp_01 = Shock_1$simulation$max_dp
yk_ds_01 = Shock_1$simulation$yk_ds
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_01 = Shock_1$simulation$yk
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un
lf_01 = Shock_1$simulation$lf
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
s_g_01 = Shock_1$simulation$s_g
ur_01 = Shock_1$simulation$ur
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
nben_g_01 = Shock_1$simulation$nben_g
yd_g_01 = Shock_1$simulation$yd_g
yh_g_01 = Shock_1$simulation$yh_g
tax_g_01 = Shock_1$simulation$tax_g
w_h_r_01 = Shock_1$simulation$w_h_r
tax_h_01 = Shock_1$simulation$tax_h
pconk_ds_01= Shock_1$simulation$pconk_ds
ik_01= Shock_1$simulation$ik
gk_01= Shock_1$simulation$gk
xk_ds_01= Shock_1$simulation$xk_ds
mk_ds_01= Shock_1$simulation$mk_ds

@@

plot(window((ur_ds_01 - ur_ds_bs1)*100, start= 2014), col= "blue", lwd=2, ylab= "percentage change", main= "Scenario 1", ylim= c(-0.05,0.04));
lines(window(((y_01 - y_bs1) / y_bs1)*100, start= 2014), col= "green", lwd=2);
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

@@

```{r}
plot(window(((nl_g_01/pc_ds_01) - (nl_g_bs1/pc_ds_bs1)), start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

>>>>

max_dp_mova=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> 
IDENTITY> alpha
EQ> alpha = 1
IF> TSLAG(wage_gap1,0) >= wage_ben_gap_mean
IDENTITY> alpha
EQ> alpha = 0
IF> TSLAG(wage_gap1,0) < wage_ben_gap_mean

@@

  shock_wage_ds_model  = TIMESERIES(c(shock_wage_ds_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens_3 = TIMESERIES(c(sens_3),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4),
   alpha = TIMESERIES(c(alpha),   
                       START=c(2005,2),FREQ=4),
  wage_ben_gap_mean = TIMESERIES(c(wage_ben_gap_mean),   
                       START=c(2005,2),FREQ=4),
  max_dp_mova = TIMESERIES(c(max_dp_mova),   
                       START=c(2005,2),FREQ=4)
  )
```

@@

S_modelData$max_dp_mova = max_dp_mova

@@

pc_ds_bs1 = Shock_bs1$simulation$pc_ds
pg_bs1 = Shock_bs1$simulation$pg

@@

```{r}
###Gengivelse af stød til model
pg_01= Shock_1$simulation$pg
inflation_01= Shock_1$simulation$inflation
pc_ds_01= Shock_1$simulation$pc_ds
alpha_01 = Shock_1$simulation$alpha
y_01= Shock_1$simulation$y
max_dp_01 = Shock_1$simulation$max_dp
yk_ds_01 = Shock_1$simulation$yk_ds
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_01 = Shock_1$simulation$yk
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un
lf_01 = Shock_1$simulation$lf
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
s_g_01 = Shock_1$simulation$s_g
ur_01 = Shock_1$simulation$ur
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
nben_g_01 = Shock_1$simulation$nben_g
yd_g_01 = Shock_1$simulation$yd_g
yh_g_01 = Shock_1$simulation$yh_g
tax_g_01 = Shock_1$simulation$tax_g
w_h_r_01 = Shock_1$simulation$w_h_r
tax_h_01 = Shock_1$simulation$tax_h
pconk_ds_01= Shock_1$simulation$pconk_ds
ik_01= Shock_1$simulation$ik
gk_01= Shock_1$simulation$gk
xk_ds_01= Shock_1$simulation$xk_ds
mk_ds_01= Shock_1$simulation$mk_ds

@@

plot(window((ur_ds_01 - ur_ds_bs1)*100, start= 2014), col= "blue", lwd=2, ylab= "percentage change", main= "Scenario 1", ylim= c(-0.05,0.04));
lines(window(((yk_01 - yk_bs1) / yk_bs1)*100, start= 2014), col= "green", lwd=2);
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

@@

```{r}
plot(window(((nl_g_01/pg_01) - (nl_g_bs1/pg_bs1)), start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
